---
title: "blogdown"
subtitle: "Create Blogs and Websites with R Markdown"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Who

- Yihui Xie, RStudio
- ~ 2 years old
- Author of `knitr` 
- Available from CRAN (version 0.17) and GitHub (development)

---

# What

Build great looking websites directly within RStudio

--

Interfaces with [Hugo](https://gohugo.io/) a fast and flexible static site generator with LOADS of themes

--

Benefits of `blogdown`

1. Produces a static website
2. Generated from RMarkdown documents

---

# How

We can build a new website using `new_site()` and choose any theme from [Hugo themes](https://themes.gohugo.io/)

```{r build_site, eval = FALSE}
library(blogdown)

new_site(theme = "bjacquemet/personal-web")
```

--

Creating new blog posts is easy

```{r new_post, eval = FALSE}
new_post("My first blog post")
```

---

# And now...

- [https://bookdown.org/yihui/blogdown](https://bookdown.org/yihui/blogdown)
- [https://ab604.github.io/docs/website_bookdown/](https://ab604.github.io/docs/website_bookdown/)
- [https://laurajanegraham.github.io/post/getting-started/](https://laurajanegraham.github.io/post/getting-started/)
- [https://www.tylerclavelle.com/code/2017/blogdown/](https://www.tylerclavelle.com/code/2017/blogdown/)


